Implicit yaddayadda

### 2011-10-27 papers/PLDI2012/implicitization.tex
Clarification sur X^d

We use another
abstract value associated to a control point $p_j$, noted $X_j^d$, which is
distinct from $X_j^s$, and initialized to $X_j^s$.

>>>>

\MM{À changer si on décide de ne plus distinguer $X^s$ et $X^d$}

To prevent the algorithm from adding too many path at a time, we
use another abstract value associated to a control point $p_j$, noted
$X_j^d$, which is distinct from $X_j^s$, and initialized to $X_j^s$.
This value is updated when a point $p_j$ is the target of a new path,
so that further SMT queries do not compute other paths with the same
source and destination if it is not needed (because these new paths
would not make $X_j^d$ grow, hence would not be returned by the SMT
solver).
